RNeXML: Parsing and Serializing the Next Generation of Phyloinformatic Data in R

### 2014-06-26 manuscripts/manuscript.Rmd
typo fix
typo fixes

NeXML already defines the `characters` element to handle descrete character traits (`nex:char`)
and the states they can assume (`nex:state`).  We will thus reuse the `characters` element for
this purpose, referring to both the character trait and the states by the ids assigned to them
in that element.  (NeXML's convention of referring to everything by id permits a single canonical
definition of each term, making it clear where additional annotation belongs).  For each edge, we 
need to indicate:

@@

The `nexml` object is an S4 object, as are all of its components (slots).  It's 
heirachical structure corresponds exactly with the XML tree of a NeXML file, with 
the single exception that both XML attributes and children are represented as slots.  
S4 objects have constructor functions to initialize them.  We create a new `nexml` 
object with the command:

>>>>

NeXML already defines the `characters` element to handle discrete character traits (`nex:char`)
and the states they can assume (`nex:state`).  We will thus reuse the `characters` element for
this purpose, referring to both the character trait and the states by the ids assigned to them
in that element.  (NeXML's convention of referring to everything by id permits a single canonical
definition of each term, making it clear where additional annotation belongs).  For each edge, we 
need to indicate:

@@

The `nexml` object is an S4 object, as are all of its components (slots).  Its 
hierarchical structure corresponds exactly with the XML tree of a NeXML file, with 
the single exception that both XML attributes and children are represented as slots.  
S4 objects have constructor functions to initialize them.  We create a new `nexml` 
object with the command:
